---
title: "Univariate Viz"
---

Use this file for practice with the **univariate viz** in-class activity.  Refer to the class website for details.

```{r}
hikes <- read.csv("https://mac-stat.github.io/data/high_peaks.csv")
```

```{r}
head(hikes)
```

#What features would we like a visualization of the categorical difficulty rating variable to capture? 
For the categorical variable rating we would like to visualize it through boxplots in order to see patterns regarding the ratings.

#What about a visualization of the quantitative elevation variable?
For a quantitative elevation variable we would preferably visualize it through a histogram.

```{r}
library(tidyverse)
ggplot(hikes, aes(x = rating))
```
# COMMENT on the change in the code and the corresponding change in the plot
```{r}
ggplot(hikes, aes(x = rating)) +
  geom_bar()
```
# COMMENT on the change in the code and the corresponding change in the plot
```{r}
ggplot(hikes, aes(x = rating)) +
  geom_bar() +
  labs(x = "Rating", y = "Number of hikes")
```
# COMMENT on the change in the code and the corresponding change in the plot
```{r}
ggplot(hikes, aes(x = rating)) +
  geom_bar(fill = "blue") +
  labs(x = "Rating", y = "Number of hikes")
```
# COMMENT on the change in the code and the corresponding change in the plot
```{r}
ggplot(hikes, aes(x = rating)) +
  geom_bar(color = "orange", fill = "blue") +
  labs(x = "Rating", y = "Number of hikes")
```
# COMMENT on the change in the code and the corresponding change in the plot
```{r}
ggplot(hikes, aes(x = rating)) +
  geom_bar(color = "orange", fill = "blue")  +
  labs(x = "Rating", y = "Number of hikes") +
  theme_minimal()
```
Part a
Reflect on the ggplot() code.

#What’s the purpose of the +? When do we use it?
The purpose of the + is to add more characteristics to the plot to define it more in depth
#We added the bars using geom_bar()? Why “geom”?
Geom because it's the function, also it's a geometric figure
#What does labs() stand for?
Labs stands for the axis and the overall plot labels
#What’s the difference between color and fill?
Color is the surrounding color, fill is the color for the inside of the bars(or lines).

#Construct a bar chart of the quantitative elevation variable.
#Explain why this might not be an effective visualization for this and other quantitative variables. (What questions does / doesn’t it help answer?)
Poor visualization because the bars don't really tell you anything too informing, this is probably the same for other quantitative variables.

```{r}
ggplot(hikes, aes(x=elevation)) +
  geom_bar(color = "pink", fill = "blue") +
  labs(x = "Elevation") +
  theme_minimal()
```
```{r}
ggplot(hikes, aes(x = elevation))
```
# COMMENT on the change in the code and the corresponding change in the plot
```{r}
ggplot(hikes, aes(x = elevation)) +
  geom_histogram()
```
# COMMENT on the change in the code and the corresponding change in the plot
```{r}
library(tidyverse)
ggplot(hikes, aes(x = elevation)) +
  geom_histogram(color = "white", fill = "blue") 
```
# COMMENT on the change in the code and the corresponding change in the plot
```{r}
ggplot(hikes, aes(x = elevation)) +
  geom_histogram(color = "white") +
  labs(x = "Elevation (feet)", y = "Number of hikes")
```
# COMMENT on the change in the code and the corresponding change in the plot
```{r}
ggplot(hikes, aes(x = elevation)) +
  geom_histogram(color = "white", binwidth = 1000) +
  labs(x = "Elevation (feet)", y = "Number of hikes")
```
# COMMENT on the change in the code and the corresponding change in the plot
```{r}
ggplot(hikes, aes(x = elevation)) +
  geom_histogram(color = "white", binwidth = 5) +
  labs(x = "Elevation (feet)", y = "Number of hikes")
```
# COMMENT on the change in the code and the corresponding change in the plot
```{r}
ggplot(hikes, aes(x = elevation)) +
  geom_histogram(color = "white", binwidth = 200) +
  labs(x = "Elevation (feet)", y = "Number of hikes")
```

```{r}
ggplot(hikes, aes(x = elevation)) +
  geom_density()
```

```{r}
ggplot(hikes, aes(x = elevation)) +
  geom_density(color = "blue")
```

```{r}
ggplot(hikes, aes(x = elevation)) +
  geom_density(fill = "orange")
```

```{r}
ggplot(hikes, aes(x = elevation)) +
geom_histogram(color = "white", binwidth = 200) +
labs(x = "Elevation (feet)", y = "Number of hikes")
```

```{r}
ggplot(hikes, aes(x = elevation)) + geom_histogram(color = "white", binwidth = 200) + labs(x = "Elevation (feet)", y = "Number of hikes")
```


